---
title: "han seurat"
output: html_document
---

Execute for init/install only

```{r}
install.packages("here")
install.packages('devtools')
install.packages("Seurat", dependencies = TRUE)


```

```{r setup, include=FALSE}

setwd("~/git/tabula-muris/")

library(here)
library(Seurat)

```

## Setup seurat object

We will analyze ~242,000 cells that were assigned a cluster ID in the original study. As a result, we don't do perform additional QC steps or filtration steps here.

```{r}

mca.matrix <- readRDS(file = here("00_data_ingest", "han_data", "MCA", "MCA_merged_mat.rds"))
mca.metadata <- read.csv(here("00_data_ingest", "han_data", "MCA", "MCA_CellAssignments.csv"), row.names = 1)

mca <- CreateSeuratObject(counts = mca.matrix, meta.data = mca.metadata, project = "MouseCellAtlas")

mca <- SubsetData(mca, cells = rownames(mca@meta.data[!is.na(mca@meta.data$ClusterID), ]), do.clean = TRUE)

mca

mca.matrix = 0

```

## Normalize Data 

You can also embed plots, for example:

```{r}

mca <- NormalizeData(object = mca, normalization.method = "LogNormalize", scale.factor = 10000)


mito.features <- grep(pattern = "^mt-", x = rownames(x = mca), value = TRUE)
percent.mito <- Matrix::colSums(x = GetAssayData(object = mca, slot = 'counts')[mito.features, ]) / Matrix::colSums(x = GetAssayData(object = mca, slot = 'counts'))
mca <- AddMetaData(object = mca, metadata = percent.mito, col.name = "percent.mito")

mca <- FindVariableFeatures(object = mca, selection.method = 'mean.var.plot', mean.cutoff = c(0.0125, 3), dispersion.cutoff = c(0.5, Inf))
length(x = VariableFeatures(object = mca))

mca <- ScaleData(object = mca, features = HVFInfo(object = mca), vars.to.regress = c("percent.mito"))

#mca <- FindVariableFeatures(object = mca, selection.method = "vst", nfeatures = 2000, verbose = FALSE)
#hv.genes <- head(rownames(mca@hvg.info), 1000)

#mito.genes <- grep(pattern = "^mt-", x = rownames(x = mca@data), value = TRUE)
#percent.mito <- Matrix::colSums(mca@raw.data[mito.genes, ])/Matrix::colSums(mca@raw.data)
#mca <- AddMetaData(object = mca, metadata = percent.mito, col.name = "percent.mito")

#mca <- ScaleData(object = mca, genes.use = hv.genes, display.progress = FALSE, vars.to.regress = "percent.mito", do.par = TRUE, num.cores = 1)

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

We now prepare tSNE and run it

```{r}

#mca <- RunPCA(object = mca, pc.genes = hv.genes, pcs.compute = 100, do.print = TRUE, pcs.print = 1:5, genes.print = 5)
mca <- RunPCA(object = mca, features = HVFInfo(object = mca), npcs=100, nfeatures.print=5, ndims.print=1:5)


mca <- RunTSNE(object = mca, reduction.use = "pca", dims.use = 1:75, tsne.method = "FIt-SNE", nthreads = 4, reduction.name = "FItSNE", reduction.key = "FItSNE_", fast_tsne_path = "/mnt/d/dev/git/FIt-SNE/bin/fast_tsne", max_iter = 2000)


mca <- RunUMAP(object = mca, reduction.use = "pca", dims.use = 1:75, min_dist = 0.75)



```



```{r}

table(Idents(mca))

table(mca@meta.data$Annotation)

```
