---
title: "FACS analysis"
output: html_document
---

```{r}

install.packages(c("useful", "ontologyIndex", "tidyverse"))

if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install("DESeq2", version = "3.8")


if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install("MAST", version = "3.8")

```

```{r include=FALSE}

library(here)
library(Seurat)
source(here("00_data_ingest", "02_tissue_analysis_rmd", "boilerplate.R"))

tissues_of_interest = c("Aorta", "Lung", "Large_Intestine", "Kidney", "Bladder", "Liver", "Brain_Non-Myeloid")

processSeurat = function(facsTiss, scale){
  facsTiss <- NormalizeData(object = facsTiss, scale.factor = scale)
  facsTiss <- ScaleData(object = facsTiss)
  
  facsTiss <- FindVariableFeatures(object = facsTiss, selection.method = 'mean.var.plot', mean.cutoff = c(0.0125, 3), dispersion.cutoff = c(0.5, Inf))

  #facsTiss <- FindVariableGenes(object = facsTiss, do.plot = TRUE, x.high.cutoff = Inf, y.cutoff = 0.5)
  facsTiss <- RunPCA(object = facsTiss, do.print = FALSE)
  
  facsTiss <- FindNeighbors(object = facsTiss)
  #facsTiss <- ProjectPCA(object = facsTiss, do.print = FALSE)
  
  facsTiss = ProjectDim(facsTiss, reduction="pca")
}

#aorta, lung, colon (large intestine), kidney, bladder and liver

```

## R Markdown

Here we are now loading the seurat objects

```{r}

all_tissues = c()

for (tissue_if_interest in tissues_of_interest){
  
    filename = here('00_data_ingest', '04_tissue_robj_generated', paste0("facs_", tissue_if_interest, "_seurat_tiss.Robj"))
    print(filename)
    load(file=filename)
    tissue_1 = UpdateSeuratObject(tiss)
  
    all_tissues = append(all_tissues, tissue_1)
}


```

## Including Plots

You can also embed plots, for example:

```{r results='asis'}

for (tissue_obj in all_tissues){
  
    plot = DimPlot(object = tissue_obj, reduction = "tsne", group.by='cell_ontology_class')
    print(plot)
}


```


```{r}

facsTiss = merge(x=all_tissues[[1]], y=all_tissues[2:length(all_tissues)], add.cell.ids=tissues_of_interest)

facsTiss <- processSeurat(facsTiss, 1e4)

n.pcs = 20
res.used <- 3

facsTiss <- FindClusters(object = facsTiss, reduction.type = "pca", dims.use = 1:n.pcs, resolution = res.used, print.output = 0, save.SNN = TRUE)
facsTiss <- RunTSNE(object = facsTiss, dims.use = 1:n.pcs, seed.use = 10, perplexity=30)



DimPlot(object = facsTiss, reduction = "tsne", group.by='cell_ontology_class')

```

```{r}

setCellIdent <- function (object, idp1, idp2) 
{
	
	cells.use <- rownames(x = object@meta.data)
	ident.use <- paste(object@meta.data[, idp1], object@meta.data[, idp2], sep=".")
	Idents(object = object, cells.use = cells.use)= ident.use
	
	return(object)
}


```


```{r}
facsTiss <- setCellIdent(object = facsTiss, idp1="orig.ident", idp2= "cell_ontology_class")

table(Idents(facsTiss))

```


Eventually we can now perform DE analysis:


```{r}

tissues_of_interest = c("Aorta", "Lung", "Large_Intestine", "Kidney", "Bladder", "Liver")

facsAortaEndo = c("Aorta.endothelial cell")
facsAortaEpi = c("Aorta.erythrocyte")

facsLungEndo = c("Lung.lung endothelial cell")
facsLungEpi = c("Lung.epithelial cell of lung")

facsLintEndo = c("Large_Intestine.enterocyte of epithelium of large intestine")
facsLintEpi = c("Large_Intestine.epithelial cell of large intestine")

facsKidneyEndo = c("Kidney.endothelial cell")
facsKidneyEpi = c("Kidney.kidney collecting duct epithelial cell","Kidney.epithelial cell of proximal tubule")

facsBladderEndo = c("Bladder.bladder urothelial cell")
facsBladderEpi = c("Bladder.bladder cell")

facsLiverEndo = c("Liver.endothelial cell of hepatic sinusoid")
facsLiverEpi = c("Liver.hepatocyte")

#newer version

facsAortaEndo = c("Aorta.endothelial cell")
facsAortaEpi = c()
facsAortaCir = c("Aorta.erythrocyte")

facsLungEndo = c("Lung.lung endothelial cell")
facsLungEpi = c("Lung.epithelial cell of lung")
facsLungCir = c("Lung.myeloid cell", "Lung.monocyte", "Lung.classical monocyte", "Lung.B cell", "Lung.T cell", "Lung.natural killer cell", "Lung.leukocyte")

facsLintEndo = c()
facsLintEpi = c("Large_Intestine.epithelial cell of large intestine")
facsLintCir = c()

facsKidneyEndo = c("Kidney.endothelial cell")
facsKidneyEpi = c()
facsKidneyCir = c("Kidney.leukocyte")

facsBladderEndo = c()
facsBladderEpi = c()
facsBladderCir = c()

facsLiverEndo = c("Liver.endothelial cell of hepatic sinusoid")
facsLiverEpi = c()
facsLiverCir = c("Liver.natural killer cell", "Liver.B cell")

facsBrainEndo = c("Brain_Non-Myeloid.endothelial cell")
facsBrainEpi = c("Brain_Non-Myeloid.brain pericyte")
facsBrainCir = c()


facsAortaCells = c(facsAortaEndo,facsAortaEpi, facsAortaCir)
facsLungCells = c(facsLungEndo,facsLungEpi, facsLungCir)
facsLintCells = c(facsLintEndo,facsLintEpi, facsLintCir)
facsKidneyCells = c(facsKidneyEndo,facsKidneyEpi, facsKidneyCir)
facsBladderCells = c(facsBladderEndo,facsBladderEpi, facsBladderCir)
facsLiverCells = c(facsLiverEndo, facsLiverEpi, facsLiverCir)
facsBrainCells = c(facsBrainEndo, facsBrainEpi, facsBrainCir)


facsAllAorta = unique(grep(pattern="Aorta", x=Idents(facsTiss), value = TRUE))
facsAllAorta = setdiff(facsAllAorta, facsAortaCells)

facsAllLung = unique(grep(pattern="Lung", x=Idents(facsTiss), value = TRUE))
facsAllLung = setdiff(facsAllLung, facsLungCells)

facsAllLint = unique(grep(pattern="Large_Intestine", x=Idents(facsTiss), value = TRUE))
facsAllLint = setdiff(facsAllLint, facsLintCells)

facsAllKidney = unique(grep(pattern="Kidney", x=Idents(facsTiss), value = TRUE))
facsAllKidney = setdiff(facsAllKidney, facsKidneyCells)

facsAllBladder = unique(grep(pattern="Bladder", x=Idents(facsTiss), value = TRUE))
facsAllBladder = setdiff(facsAllBladder, facsBladderCells)

facsAllLiver = unique(grep(pattern="Liver", x=Idents(facsTiss), value = TRUE))
facsAllLiver = setdiff(facsAllLiver, facsLiverCells)

facsAllBrain = unique(grep(pattern="Brain", x=Idents(facsTiss), value = TRUE))
facsAllBrain = setdiff(facsAllBrain, facsBrainCells)

```

```{r}


print(facsAortaCells)
print(facsLungCells)
print(facsKidneyCells)
print(facsBladderCells)
print(facsLiverCells)
print(facsBrainCells)

print(facsAllAorta)
print(facsAllLung)
print(facsAllKidney)
print(facsAllBladder)
print(facsAllLiver)
print(facsAllBrain)


```

We should prepare our functions again ....

```{r}

makeAnalysis <- function( tissues1, tissues2)
{
  
    if (is.null(tissues1)|| is.null(tissues2))
    {
      print("makeAnalysis failed due to null tissue")
      return(NULL)
    }
  
    if (length(tissues1) == 0 || length(tissues2) == 0)
    {
      print("makeAnalysis failed due to 0 length tissue")
      return(NULL)
    }
  
    print(tissues1)
    print(tissues2)
  
    newMarkers = FindMarkers(facsTiss, ident.1=tissues1, ident.2=tissues2,only.pos=TRUE, test.use="MAST")
    return(newMarkers)
}

```


Now we can run the analysis against each other ...

# Analysis: Endothelial Cells against each other




## Aorta
```{r}


facs_endo_aorta_lung = makeAnalysis(facsAortaEndo, facsLungEndo)

write.table(facs_endo_aorta_lung, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("facs_endo_aorta_lung", ".tsv", sep="")) ,quote=FALSE, sep='\t')

facs_endo_aorta_kidney = makeAnalysis(facsAortaEndo, facsKidneyEndo)

write.table(facs_endo_aorta_kidney, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("facs_endo_aorta_kidney", ".tsv", sep="")) ,quote=FALSE, sep='\t')


facs_endo_aorta_liver = makeAnalysis(facsAortaEndo, facsLiverEndo)

write.table(facs_endo_aorta_liver, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("facs_endo_aorta_liver", ".tsv", sep="")) ,quote=FALSE, sep='\t')


facs_endo_aorta_brain = makeAnalysis(facsAortaEndo, facsBrainEndo)

write.table(facs_endo_aorta_brain, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("facs_endo_aorta_brain", ".tsv", sep="")) ,quote=FALSE, sep='\t')


facs_endo_aorta_all = makeAnalysis(facsAortaEndo, c(facsLungEndo, facsKidneyEndo, facsLiverEndo, facsBrainEndo))

write.table(facs_endo_aorta_all, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("facs_endo_aorta_all", ".tsv", sep="")) ,quote=FALSE, sep='\t')

```

## Lung
```{r}


facs_endo_lung_aorta = makeAnalysis(facsLungEndo, facsAortaEndo)

write.table(facs_endo_lung_aorta, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("facs_endo_lung_aorta", ".tsv", sep="")) ,quote=FALSE, sep='\t')

facs_endo_lung_kidney = makeAnalysis(facsLungEndo, facsKidneyEndo)

write.table(facs_endo_lung_kidney, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("facs_endo_lung_kidney", ".tsv", sep="")) ,quote=FALSE, sep='\t')


facs_endo_lung_liver = makeAnalysis(facsLungEndo, facsLiverEndo)

write.table(facs_endo_lung_liver, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("facs_endo_lung_liver", ".tsv", sep="")) ,quote=FALSE, sep='\t')


facs_endo_lung_brain = makeAnalysis(facsLungEndo, facsBrainEndo)

write.table(facs_endo_lung_brain, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("facs_endo_lung_brain", ".tsv", sep="")) ,quote=FALSE, sep='\t')


facs_endo_lung_all = makeAnalysis(facsLungEndo, c(facsAortaEndo, facsKidneyEndo, facsLiverEndo, facsBrainEndo))

write.table(facs_endo_lung_all, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("facs_endo_lung_all", ".tsv", sep="")) ,quote=FALSE, sep='\t')

```


## Kidney
```{r}


facs_endo_kidney_aorta = makeAnalysis(facsKidneyEndo, facsAortaEndo)

write.table(facs_endo_kidney_aorta, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("facs_endo_kidney_aorta", ".tsv", sep="")) ,quote=FALSE, sep='\t')

facs_endo_kidney_lung = makeAnalysis(facsKidneyEndo, facsLungEndo)

write.table(facs_endo_kidney_lung, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("facs_endo_kidney_lung", ".tsv", sep="")) ,quote=FALSE, sep='\t')


facs_endo_kidney_liver = makeAnalysis(facsKidneyEndo, facsLiverEndo)

write.table(facs_endo_kidney_liver, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("facs_endo_kidney_liver", ".tsv", sep="")) ,quote=FALSE, sep='\t')


facs_endo_kidney_brain = makeAnalysis(facsKidneyEndo, facsBrainEndo)

write.table(facs_endo_kidney_brain, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("facs_endo_kidney_brain", ".tsv", sep="")) ,quote=FALSE, sep='\t')


facs_endo_kidney_all = makeAnalysis(facsKidneyEndo, c(facsAortaEndo, facsLungEndo, facsLiverEndo, facsBrainEndo))

write.table(facs_endo_kidney_all, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("facs_endo_kidney_all", ".tsv", sep="")) ,quote=FALSE, sep='\t')

```


## Liver
```{r}


facs_endo_liver_aorta = makeAnalysis(facsLiverEndo, facsAortaEndo)

write.table(facs_endo_liver_aorta, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("facs_endo_liver_aorta", ".tsv", sep="")) ,quote=FALSE, sep='\t')

facs_endo_liver_lung = makeAnalysis(facsLiverEndo, facsLungEndo)

write.table(facs_endo_liver_lung, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("facs_endo_liver_lung", ".tsv", sep="")) ,quote=FALSE, sep='\t')


facs_endo_liver_kidney = makeAnalysis(facsLiverEndo, facsKidneyEndo)

write.table(facs_endo_liver_kidney, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("facs_endo_liver_kidney", ".tsv", sep="")) ,quote=FALSE, sep='\t')


facs_endo_liver_brain = makeAnalysis(facsLiverEndo, facsBrainEndo)

write.table(facs_endo_liver_brain, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("facs_endo_liver_brain", ".tsv", sep="")) ,quote=FALSE, sep='\t')


facs_endo_liver_all = makeAnalysis(facsLiverEndo, c(facsAortaEndo, facsLungEndo, facsKidneyEndo, facsBrainEndo))

write.table(facs_endo_liver_all, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("facs_endo_liver_all", ".tsv", sep="")) ,quote=FALSE, sep='\t')

```


## Brain
```{r}


facs_endo_brain_aorta = makeAnalysis(facsBrainEndo, facsAortaEndo)

write.table(facs_endo_brain_aorta, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("facs_endo_brain_aorta", ".tsv", sep="")) ,quote=FALSE, sep='\t')

facs_endo_brain_lung = makeAnalysis(facsBrainEndo, facsLungEndo)

write.table(facs_endo_brain_lung, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("facs_endo_brain_lung", ".tsv", sep="")) ,quote=FALSE, sep='\t')


facs_endo_brain_kidney = makeAnalysis(facsBrainEndo, facsKidneyEndo)

write.table(facs_endo_brain_kidney, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("facs_endo_brain_kidney", ".tsv", sep="")) ,quote=FALSE, sep='\t')


facs_endo_brain_liver = makeAnalysis(facsBrainEndo, facsLiverEndo)

write.table(facs_endo_brain_liver, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("facs_endo_brain_liver", ".tsv", sep="")) ,quote=FALSE, sep='\t')


facs_endo_brain_all = makeAnalysis(facsBrainEndo, c(facsAortaEndo, facsLungEndo, facsKidneyEndo, facsLiverEndo))

write.table(facs_endo_brain_all, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("facs_endo_brain_all", ".tsv", sep="")) ,quote=FALSE, sep='\t')

```




## Aorta vs Lung

```{r}

aorta_lung_markers_facs = makeAnalysis(facsAortaEndo, facsLungEndo)

write.table(aorta_lung_markers_facs, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("aorta_lung_markers_facs", ".tsv", sep="")) ,quote=FALSE, sep='\t')
```

## Aorta vs Lint

```{r}

aorta_lint_markers_facs = makeAnalysis(facsAortaEndo, facsLintEndo)

write.table(aorta_lint_markers_facs, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("aorta_lint_markers_facs",".tsv", sep="")) ,quote=FALSE, sep='\t')
```

## Aorta vs Kidney
```{r}

aorta_kidney_markers_facs = makeAnalysis(facsAortaEndo, facsKidneyEndo)

write.table(aorta_kidney_markers_facs, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("aorta_kidney_markers_facs", ".tsv", sep="")) ,quote=FALSE, sep='\t')
```

## Aorta vs Bladder

```{r}

aorta_bladder_markers_facs = makeAnalysis(facsAortaEndo, facsBladderEndo)

write.table(aorta_bladder_markers_facs, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("aorta_bladder_markers_facs", ".tsv", sep="")) ,quote=FALSE, sep='\t')
```

## Aorta vs Liver

```{r}

aorta_liver_markers_facs = makeAnalysis(facsAortaEndo, facsLiverEndo)

write.table(aorta_liver_markers_facs, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("aorta_liver_markers_facs", ".tsv", sep="")) ,quote=FALSE, sep='\t')
```

## Lung vs Lint

```{r}

lung_lint_markers_facs = makeAnalysis(facsLungEndo, facsLintEndo)

write.table(lung_lint_markers_facs, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("lung_lint_markers_facs",".tsv", sep="")) ,quote=FALSE, sep='\t')
```

## Lung vs Kidney
```{r}

lung_kidney_markers_facs = makeAnalysis(facsLungEndo, facsKidneyEndo)

write.table(lung_kidney_markers_facs, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("lung_kidney_markers_facs", ".tsv", sep="")) ,quote=FALSE, sep='\t')
```

## Lung vs Bladder

```{r}

lung_bladder_markers_facs = makeAnalysis(facsLungEndo, facsBladderEndo)

write.table(lung_bladder_markers_facs, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("lung_bladder_markers_facs", ".tsv", sep="")) ,quote=FALSE, sep='\t')
```

## Lung vs Liver

```{r}

lung_liver_markers_facs = makeAnalysis(facsLungEndo, facsLiverEndo)

write.table(lung_liver_markers_facs, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("lung_liver_markers_facs", ".tsv", sep="")) ,quote=FALSE, sep='\t')
```


## Lint vs Kidney

```{r}

lint_kidney_markers_facs = makeAnalysis(facsLintEndo, facsKidneyEndo)

write.table(lint_kidney_markers_facs, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("lint_kidney_markers_facs", ".tsv", sep="")) ,quote=FALSE, sep='\t')
```

## Lint vs Bladder

```{r}

lint_bladder_markers_facs = makeAnalysis(facsLintEndo, facsBladderEndo)

write.table(lint_bladder_markers_facs, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("lint_bladder_markers_facs", ".tsv", sep="")) ,quote=FALSE, sep='\t')
```

## Lint vs Liver
```{r}

lint_liver_markers_facs = makeAnalysis(facsLintEndo, facsLiverEndo)

write.table(lint_liver_markers_facs, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("lint_liver_markers_facs", ".tsv", sep="")) ,quote=FALSE, sep='\t')
```

## Kidney vs Bladder
```{r}

kidney_bladder_markers_facs = makeAnalysis(facsKidneyEndo, facsBladderEndo)

write.table(kidney_bladder_markers_facs, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("kidney_bladder_markers_facs", ".tsv", sep="")) ,quote=FALSE, sep='\t')
```

## Kidney vs Liver

```{r}

kidney_liver_markers_facs = makeAnalysis(facsKidneyEndo, facsLiverEndo)

write.table(kidney_liver_markers_facs, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("kidney_liver_markers_facs", ".tsv", sep="")) ,quote=FALSE, sep='\t')
```

## Bladder vs Liver
```{r}

bladder_liver_markers_facs = makeAnalysis(facsBladderEndo, facsLiverEndo)

write.table(bladder_liver_markers_facs, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("bladder_liver_markers_facs", ".tsv", sep="")) ,quote=FALSE, sep='\t')
```

# Analysis same organ, endo vs epi

## Aorta Endo vs Aorta Epi
```{r}

aorta_endopi_markers_facs = makeAnalysis(facsAortaEndo, facsAortaEpi)

write.table(aorta_endopi_markers_facs, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("aorta_endopi_markers_facs", ".tsv", sep="")) ,quote=FALSE, sep='\t')

```

## Bladder Endo vs Bladder Epi
```{r}

bladder_endopi_markers_facs = makeAnalysis(facsBladderEndo, facsBladderEpi)

write.table(bladder_endopi_markers_facs, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("bladder_endopi_markers_facs", ".tsv", sep="")) ,quote=FALSE, sep='\t')

```

## Kidney Endo vs Kidney Epi
```{r}

kidney_endopi_markers_facs = makeAnalysis(facsKidneyEndo, facsKidneyEpi)

write.table(kidney_endopi_markers_facs, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("kidney_endopi_markers_facs", ".tsv", sep="")) ,quote=FALSE, sep='\t')

```

## Lint Endo vs Lint Epi
```{r}

lint_endopi_markers_facs = makeAnalysis(facsLintEndo, facsLintEpi)

write.table(lint_endopi_markers_facs, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("lint_endopi_markers_facs", ".tsv", sep="")) ,quote=FALSE, sep='\t')

```

## Liver Endo vs Liver Epi
```{r}

liver_endopi_markers_facs = makeAnalysis(facsLiverEndo, facsLiverEpi)

write.table(liver_endopi_markers_facs, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("liver_endopi_markers_facs", ".tsv", sep="")) ,quote=FALSE, sep='\t')

```

## Lung Endo vs Lung Epi
```{r}

lung_endopi_markers_facs = makeAnalysis(facsLungEndo, facsLungEpi)

write.table(lung_endopi_markers_facs, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("lung_endopi_markers_facs", ".tsv", sep="")) ,quote=FALSE, sep='\t')

```

# Analysis same organ, endo vs rest+epi

## Aorta Endo

```{r}

aorta_endo_rest_markers_facs = makeAnalysis(facsAortaEndo, unique(c(facsAllAorta, facsAortaEpi)))

write.table(aorta_endo_rest_markers_facs, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("aorta_endo_rest_markers_facs", ".tsv", sep="")) ,quote=FALSE, sep='\t')

```
## Bladder Endo

```{r}

bladder_endo_rest_markers_facs = makeAnalysis(facsBladderEndo, unique(c(facsAllBladder, facsBladderEpi)))

write.table(bladder_endo_rest_markers_facs, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("bladder_endo_rest_markers_facs", ".tsv", sep="")) ,quote=FALSE, sep='\t')

```

## Kidney Endo

```{r}

kidney_endo_rest_markers_facs = makeAnalysis(facsKidneyEndo, unique(c(facsAllKidney, facsKidneyEpi)))

write.table(kidney_endo_rest_markers_facs, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("kidney_endo_rest_markers_facs", ".tsv", sep="")) ,quote=FALSE, sep='\t')

```

## Lint Endo

```{r}

lint_endo_rest_markers_facs = makeAnalysis(facsLintEndo, unique(c(facsAllLint, facsLintEpi)))

write.table(lint_endo_rest_markers_facs, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("lint_endo_rest_markers_facs", ".tsv", sep="")) ,quote=FALSE, sep='\t')

```

## Liver Endo

```{r}

liver_endo_rest_markers_facs = makeAnalysis(facsLiverEndo, unique(c(facsAllLiver, facsLiverEpi)))

write.table(liver_endo_rest_markers_facs, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("liver_endo_rest_markers_facs", ".tsv", sep="")) ,quote=FALSE, sep='\t')

```

## Lung Endo

```{r}


lung_endo_rest_markers_facs = makeAnalysis(facsLungEndo, unique(c(facsAllLung, facsLungEpi)))

write.table(lung_endo_rest_markers_facs, file = here("00_data_ingest", "sanne_analysis", "facs_analysis", paste("lung_endo_rest_markers_facs", ".tsv", sep="")) ,quote=FALSE, sep='\t')

```

```{r, fig.width=12, fig.height=20}

VlnPlot(object = facsTiss, features = c("Ehd3", "Emcn", "Fabp4", "Fxyd2", "Gpx3", "Igfbp5", "Kap", "Klk1", "Miox", "Pbx1", "Plat", "Plscr2", "Plvap", "Rsad2", "Thbd", "Tspan13"), ncol=4, idents=unique(c(facsKidneyEndo,facsAortaEndo, facsLungEndo, facsLiverEndo, facsBrainEndo)), slot = 'counts', log = TRUE, same.y.lims =FALSE)

```




# NEW ANALYSIS

```{r}

makeNewAnalysisFacs = function(targetCells, sourceCells, tissueName, prefix) {
    if (is.null(targetCells)|| is.null(sourceCells))
    {
      print("makeAnalysis failed due to null tissue")
      return(NULL)
    }
  
    if (length(targetCells) == 0 || length(sourceCells) == 0)
    {
      print("makeAnalysis failed due to 0 length tissue")
      return(NULL)
    }
  
  
  allComparisons = c()
  
  for (targetCell in targetCells)
  {
    
    targetComparisons = c()
  
    for (sourceCell in sourceCells)
    {
      
      print(targetCell)
      print(sourceCell)
      
      newMarkers = FindMarkers(facsTiss, ident.1=c(targetCell), ident.2=c(sourceCell),only.pos=FALSE, test.use="MAST")
      
      
      
      outfname = gsub(" ", "_", paste(prefix, paste(tissueName, targetCell, sourceCell, sep = "___"), ".tsv", sep=""))
      print(outfname)
      
      write.table(newMarkers, file = here("00_data_ingest", "sanne_analysis", "facs_analysis_excl", outfname) ,quote=FALSE, sep='\t')
      
      targetComparisons = append(targetComparisons, list(newMarkers))
      
    }

    allComparisons = append(allComparisons, list(targetComparisons))
    
  }
  
  return(allComparisons)
}

```

## WITHIN OWN TISSUE

```{r results="hide", echo=FALSE}

a = makeNewAnalysisFacs(facsKidneyEndo, c(facsKidneyCir, facsKidneyEpi, facsAllKidney), "kidney", "excl_")
a = makeNewAnalysisFacs(facsLungEndo, c(facsLungCir, facsLungEpi, facsAllLung), "lung", "excl_")
a = makeNewAnalysisFacs(facsAortaEndo, c(facsAortaCir, facsAortaEpi, facsAllAorta), "aorta", "excl_")
a = makeNewAnalysisFacs(facsBladderEndo, c(facsBladderCir, facsBladderEpi, facsAllBladder), "bladder", "excl_")
a = makeNewAnalysisFacs(facsLiverEndo, c(facsLiverCir, facsLiverEpi, facsAllLiver), "liver", "excl_")
a = makeNewAnalysisFacs(facsBrainEndo, c(facsBrainCir, facsBrainEpi, facsAllBrain), "brain", "excl_")

```

## WITHIN OWN CLASS

```{r results="hide", echo=FALSE}

a=makeNewAnalysisFacs(facsKidneyEndo, c(facsLungEndo, facsAortaEndo, facsBladderEndo, facsLiverEndo, facsBrainEndo), "kidney", "endo_excl_")
a=makeNewAnalysisFacs(facsLungEndo, c(facsKidneyEndo, facsAortaEndo, facsBladderEndo, facsLiverEndo, facsBrainEndo), "lung", "endo_excl_")
a=makeNewAnalysisFacs(facsAortaEndo, c(facsLungEndo, facsKidneyEndo, facsBladderEndo, facsLiverEndo, facsBrainEndo), "aorta", "endo_excl_")
a=makeNewAnalysisFacs(facsBladderEndo, c(facsAortaEndo, facsLungEndo, facsKidneyEndo, facsLiverEndo, facsBrainEndo), "bladder", "endo_excl_")
a=makeNewAnalysisFacs(facsLiverEndo, c(facsAortaEndo, facsLungEndo, facsKidneyEndo, facsBladderEndo, facsBrainEndo), "liver", "endo_excl_")
a=makeNewAnalysisFacs(facsBrainEndo, c(facsAortaEndo, facsLungEndo, facsKidneyEndo, facsBladderEndo, facsLiverEndo), "brain", "endo_excl_")

```


## AGAINST ALL OTHER BLOOD CIRCULATING STUFF

```{r results="hide", echo=FALSE}
a=makeNewAnalysisFacs(facsKidneyEndo, c(facsKidneyCir, facsLungCir, facsAortaCir, facsBladderCir, facsLiverCir, facsBrainCir), "kidney", "endo_cir_excl_")
a=makeNewAnalysisFacs(facsLungEndo, c(facsLungCir, facsKidneyCir, facsAortaCir, facsBladderCir, facsLiverCir, facsBrainCir), "lung", "endo_cir_excl_")
a=makeNewAnalysisFacs(facsAortaEndo, c(facsAortaCir, facsLungCir, facsKidneyCir, facsBladderCir, facsLiverCir, facsBrainCir), "aorta", "endo_cir_excl_")
a=makeNewAnalysisFacs(facsBladderEndo, c(facsBladderCir, facsAortaCir, facsLungCir, facsKidneyCir, facsLiverCir, facsBrainCir), "bladder", "endo_cir_excl_")
a=makeNewAnalysisFacs(facsLiverEndo, c(facsLiverCir, facsAortaCir, facsLungCir, facsKidneyCir, facsBladderCir, facsBrainCir), "liver", "endo_cir_excl_")
a=makeNewAnalysisFacs(facsBrainEndo, c(facsLiverCir, facsAortaCir, facsLungCir, facsKidneyCir, facsBladderCir, facsBrainCir), "brain", "endo_cir_excl_")
```

## AGAINST ALL OTHER EPITHELIAL

```{r results="hide", echo=FALSE}
a=makeNewAnalysisFacs(facsKidneyEndo, c(facsKidneyEpi, facsLungEpi, facsAortaEpi, facsBladderEpi, facsLiverEpi, facsBrainEpi), "kidney", "endo_epi_excl_")
a=makeNewAnalysisFacs(facsLungEndo, c(facsLungEpi, facsKidneyEpi, facsAortaEpi, facsBladderEpi, facsLiverEpi, facsBrainEpi), "lung", "endo_epi_excl_")
a=makeNewAnalysisFacs(facsAortaEndo, c(facsAortaEpi, facsLungEpi, facsKidneyEpi, facsBladderEpi, facsLiverEpi, facsBrainEpi), "aorta", "endo_epi_excl_")
a=makeNewAnalysisFacs(facsBladderEndo, c(facsBladderEpi, facsAortaEpi, facsLungEpi, facsKidneyEpi, facsLiverEpi, facsBrainEpi), "bladder", "endo_epi_excl_")
a=makeNewAnalysisFacs(facsLiverEndo, c(facsLiverEpi, facsAortaEpi, facsLungEpi, facsKidneyEpi, facsBladderEpi, facsBrainEpi), "liver", "endo_epi_excl_")
a=makeNewAnalysisFacs(facsBrainEndo, c(facsLiverEpi, facsAortaEpi, facsLungEpi, facsKidneyEpi, facsBladderEpi, facsBrainEpi), "brain", "endo_epi_excl_")
```



## AGAINST ALL 

```{r results="hide", echo=FALSE, message=F, warning=F}
a=makeNewAnalysisFacs(facsKidneyEndo, c(facsKidneyEpi, facsLungEpi, facsAortaEpi, facsBladderEpi, facsLiverEpi,facsKidneyCir, facsLungCir, facsAortaCir, facsBladderCir, facsLiverCir, facsBrainEpi, facsBrainCir), "kidney", "endo_cirepi_excl_")
a=makeNewAnalysisFacs(facsLungEndo, c(facsKidneyEpi, facsLungEpi, facsAortaEpi, facsBladderEpi, facsLiverEpi,facsLungCir, facsKidneyCir, facsAortaCir, facsBladderCir, facsLiverCir, facsBrainEpi, facsBrainCir), "lung", "endo_cirepi_excl_")
a=makeNewAnalysisFacs(facsAortaEndo, c(facsKidneyEpi, facsLungEpi, facsAortaEpi, facsBladderEpi, facsLiverEpi,facsAortaCir, facsLungCir, facsKidneyCir, facsBladderCir, facsLiverCir, facsBrainEpi, facsBrainCir), "aorta", "endo_cirepi_excl_")
a=makeNewAnalysisFacs(facsBladderEndo, c(facsKidneyEpi, facsLungEpi, facsAortaEpi, facsBladderEpi, facsLiverEpi,facsBladderCir, facsAortaCir, facsLungCir, facsKidneyCir, facsLiverCir, facsBrainEpi, facsBrainCir), "bladder", "endo_cirepi_excl_")
a=makeNewAnalysisFacs(facsLiverEndo, c(facsKidneyEpi, facsLungEpi, facsAortaEpi, facsBladderEpi, facsLiverEpi,facsLiverCir, facsAortaCir, facsLungCir, facsKidneyCir, facsBladderCir, facsBrainEpi, facsBrainCir), "liver", "endo_cirepi_excl_")
a=makeNewAnalysisFacs(facsBrainEndo, c(facsKidneyEpi, facsLungEpi, facsAortaEpi, facsBladderEpi, facsLiverEpi,facsLiverCir, facsAortaCir, facsLungCir, facsKidneyCir, facsBladderCir, facsBrainEpi, facsBrainCir), "brain", "endo_cirepi_excl_")
```



