---
title: "han seurat"
output: html_document
---

```{r setup, include=FALSE}

setwd("~/git/tabula-muris/")

library(here)
library(Seurat)

```

If the mca object is not loaded, load it now!

```{r}

#load(here("00_data_ingest", "sanne_analysis", "wells_han_data"))

```

## Identify interesting cells per tissue


We must first define the set of interesting tissues/cells


```{r}

tissues_of_interest = c("Aorta", "Lung", "Large_Intestine", "Kidney", "Bladder", "Liver")

aortaEndo = c("Vascular endothelial cell(Neonatal-Heart)", "Endothelial cell_Eln high(Neonatal-Heart)", "Endothelial cell_Enpp2 high(Neonatal-Heart)", "Endothelial cell_Igfbp5 high(Neonatal-Heart)")
aortaEpi = c("Epithelial cell(Neonatal-Heart)")

lungEndo = c("Endothelial cell_Kdr high(Lung)", "Endothelial cell_Tmem100 high(Lung)", "Endothelial cells_Vwf high(Lung)")
lungEpi = c("Epithelial cell_Sftpc high(Fetal_Lung)", "Epithelial cell_Aldh1a2_high(Fetal_Lung)")

lintEndo = c("Enteroendocrine(Fetal_Intestine)", "Endothelial cell(Fetal_Intestine)")
lintEpi = c("Epithelium of small intestinal villi_Fabp1 high(Small-Intestine)",
"Columnar epithelium(Small-Intestine)",
"Epithelium of small intestinal villi_Fabp6 high(Small-Intestine)",
"Epithelial cell_Kcne3 high(Small-Intestine)",
"Epithelial cell_Sh2d6 high(Small-Intestine)",
"Epithelium of small intestinal villi_S100g high(Small-Intestine)",
"Epithelium of small intestinal villi_Gm23935 high(Small-Intestine)",
"Epithelium of small intestinal villi_mt-Nd1 high(Small-Intestine)")

kidneyEndo = c("Endothelial cell(Kidney)","Fenestrated endothelial cell_Plvap high(Kidney)", "Fenestrated endothelial cell_Tm4sf1 high(Kidney)" )
kidneyEpi = c("Ureteric epithelium(Kidney)", "Epithelial cell_Cryab high(Kidney)", "Glomerular epithelial cell_Aldh1a2 high(Fetal_Kidney)")

bladderEndo = c("Urothelium(Bladder)", "Vascular endothelial cell(Bladder)","Endothelial cell_Ly6c1 high(Bladder)")
bladderEpi = c("Basal epithelial cell(Bladder)", "Epithelial cell_Upk3a high(Bladder)", "Epithelial cell_Gm23935 high(Bladder)")

liverEndo = c("Endothelial cell(Liver)")
liverEpi = c("Epithelial cell(Liver)", "Epithelia cell_Spp1 high(Liver)")


aortaCells = c(aortaEndo,aortaEpi)
lungCells = c(lungEndo,lungEpi)
lintCells = c(lintEndo,lintEpi)
kidneyCells = c(kidneyEndo,kidneyEpi)
bladderCells = c(bladderEndo,bladderEpi)
liverCells = c(liverEndo, liverEpi)


allAorta = unique(grep(pattern="Neonatal-Heart", x=mca@meta.data$Annotation, value = TRUE))
allAorta = setdiff(allAorta, aortaCells)

allLung = unique(grep(pattern="Lung", x=mca@meta.data$Annotation, value = TRUE))
allLung = setdiff(allLung, lungCells)

allLint = unique(grep(pattern="[Small|Fetal][_-]Intestine", x=mca@meta.data$Annotation, value = TRUE))
allLint = setdiff(allLint, lintCells)

allKidney = unique(grep(pattern="Kidney", x=mca@meta.data$Annotation, value = TRUE))
allKidney = setdiff(allKidney, kidneyCells)

allBladder = unique(grep(pattern="Bladder", x=mca@meta.data$Annotation, value = TRUE))
allBladder = setdiff(allBladder, bladderCells)

allLiver = unique(grep(pattern="Liver", x=mca@meta.data$Annotation, value = TRUE))
allLiver = setdiff(allLiver, liverCells)


```

Define the analysis
```{r}

makeAnalysis <- function( tissues1, tissues2)
{
    newMarkers = FindMarkers(mca, ident.1=tissues1, ident.2=tissues2,only.pos=TRUE, test.use="MAST")
    return(newMarkers)
}

```

Prepare the analysis

```{r}
setCellIdent <- function (object, idp1) 
{
	
	cells.use <- rownames(x = object@meta.data)
	ident.use <- object@meta.data[, idp1]
	Idents(object = object, cells.use = cells.use)= ident.use
	
	return(object)
}


mca <- setCellIdent(object = mca, "Annotation")

```

Now we can run the analysis against each other ...

# Analysis: Endothelial Cells against each other


## Aorta vs Lung

```{r}

aorta_lung_markers_wells = makeAnalysis(aortaEndo, lungEndo)

write.table(aorta_lung_markers_wells, file = here("00_data_ingest", "sanne_analysis", "wells_analysis", "aorta_lung_markers_wells.tsv") ,quote=FALSE, sep='\t')
```

## Aorta vs Lint

```{r}

aorta_lint_markers_wells = makeAnalysis(aortaEndo, lintEndo)

write.table(aorta_lint_markers_wells, file = here("00_data_ingest", "sanne_analysis", "wells_analysis", "aorta_lint_markers_wells.tsv") ,quote=FALSE, sep='\t')
```

## Aorta vs Kidney
```{r}

aorta_kidney_markers_wells = makeAnalysis(aortaEndo, kidneyEndo)

write.table(aorta_kidney_markers_wells, file = here("00_data_ingest", "sanne_analysis", "wells_analysis", paste("aorta_kidney_markers_wells", ".tsv", sep="")) ,quote=FALSE, sep='\t')
```

## Aorta vs Bladder

```{r}

aorta_bladder_markers_wells = makeAnalysis(aortaEndo, bladderEndo)

write.table(aorta_bladder_markers_wells, file = here("00_data_ingest", "sanne_analysis", "wells_analysis", paste("aorta_bladder_markers_wells", ".tsv", sep="")) ,quote=FALSE, sep='\t')
```

## Aorta vs Liver

```{r}

aorta_liver_markers_wells = makeAnalysis(aortaEndo, liverEndo)

write.table(aorta_liver_markers_wells, file = here("00_data_ingest", "sanne_analysis", "wells_analysis", paste("aorta_liver_markers_wells", ".tsv", sep="")) ,quote=FALSE, sep='\t')
```
## Lung vs Lint

```{r}

lung_lint_markers_wells = makeAnalysis(lungEndo, lintEndo)

write.table(lung_lint_markers_wells, file = here("00_data_ingest", "sanne_analysis", "wells_analysis", paste("lung_lint_markers_wells",".tsv", sep="")) ,quote=FALSE, sep='\t')
```

## Lung vs Kidney
```{r}

lung_kidney_markers_wells = makeAnalysis(lungEndo, kidneyEndo)

write.table(lung_kidney_markers_wells, file = here("00_data_ingest", "sanne_analysis", "wells_analysis", paste("lung_kidney_markers_wells", ".tsv", sep="")) ,quote=FALSE, sep='\t')
```

## Lung vs Bladder

```{r}

lung_bladder_markers_wells = makeAnalysis(lungEndo, bladderEndo)

write.table(lung_bladder_markers_wells, file = here("00_data_ingest", "sanne_analysis", "wells_analysis", paste("lung_bladder_markers_wells", ".tsv", sep="")) ,quote=FALSE, sep='\t')
```

## Lung vs Liver

```{r}

lung_liver_markers_wells = makeAnalysis(lungEndo, liverEndo)

write.table(lung_liver_markers_wells, file = here("00_data_ingest", "sanne_analysis", "wells_analysis", paste("lung_liver_markers_wells", ".tsv", sep="")) ,quote=FALSE, sep='\t')
```



## Lint vs Kidney

```{r}

lint_kidney_markers_wells = makeAnalysis(lintEndo, kidneyEndo)

write.table(lint_kidney_markers_wells, file = here("00_data_ingest", "sanne_analysis", "wells_analysis", paste("lint_kidney_markers_wells", ".tsv", sep="")) ,quote=FALSE, sep='\t')
```

## Lint vs Bladder

```{r}

lint_bladder_markers_wells = makeAnalysis(lintEndo, bladderEndo)

write.table(lint_bladder_markers_wells, file = here("00_data_ingest", "sanne_analysis", "wells_analysis", paste("lint_bladder_markers_wells", ".tsv", sep="")) ,quote=FALSE, sep='\t')
```

## Lint vs Liver
```{r}

lint_liver_markers_wells = makeAnalysis(lintEndo, liverEndo)

write.table(lint_liver_markers_wells, file = here("00_data_ingest", "sanne_analysis", "wells_analysis", paste("lint_liver_markers_wells", ".tsv", sep="")) ,quote=FALSE, sep='\t')
```

## Kidney vs Bladder
```{r}

kidney_bladder_markers_wells = makeAnalysis(kidneyEndo, bladderEndo)

write.table(kidney_bladder_markers_wells, file = here("00_data_ingest", "sanne_analysis", "wells_analysis", paste("kidney_bladder_markers_wells", ".tsv", sep="")) ,quote=FALSE, sep='\t')
```

## Kidney vs Liver

```{r}

kidney_liver_markers_wells = makeAnalysis(kidneyEndo, liverEndo)

write.table(kidney_liver_markers_wells, file = here("00_data_ingest", "sanne_analysis", "wells_analysis", paste("kidney_liver_markers_wells", ".tsv", sep="")) ,quote=FALSE, sep='\t')
```

## Bladder vs Liver
```{r}

bladder_liver_markers_wells = makeAnalysis(bladderEndo, liverEndo)

write.table(bladder_liver_markers_wells, file = here("00_data_ingest", "sanne_analysis", "wells_analysis", paste("bladder_liver_markers_wells", ".tsv", sep="")) ,quote=FALSE, sep='\t')
```

# Analysis same organ, endo vs epi

## Aorta Endo vs Aorta Epi
```{r}

aorta_endopi_markers_wells = makeAnalysis(aortaEndo, aortaEpi)

write.table(aorta_endopi_markers_wells, file = here("00_data_ingest", "sanne_analysis", "wells_analysis", paste("aorta_endopi_markers_wells", ".tsv", sep="")) ,quote=FALSE, sep='\t')

```

## Bladder Endo vs Bladder Epi
```{r}

bladder_endopi_markers_wells = makeAnalysis(bladderEndo, bladderEpi)

write.table(bladder_endopi_markers_wells, file = here("00_data_ingest", "sanne_analysis", "wells_analysis", paste("bladder_endopi_markers_wells", ".tsv", sep="")) ,quote=FALSE, sep='\t')

```

## Kidney Endo vs Kidney Epi
```{r}

kidney_endopi_markers_wells = makeAnalysis(kidneyEndo, kidneyEpi)

write.table(kidney_endopi_markers_wells, file = here("00_data_ingest", "sanne_analysis", "wells_analysis", paste("kidney_endopi_markers_wells", ".tsv", sep="")) ,quote=FALSE, sep='\t')

```

## Lint Endo vs Lint Epi
```{r}

lint_endopi_markers_wells = makeAnalysis(lintEndo, lintEpi)

write.table(lint_endopi_markers_wells, file = here("00_data_ingest", "sanne_analysis", "wells_analysis", paste("lint_endopi_markers_wells", ".tsv", sep="")) ,quote=FALSE, sep='\t')

```

## Liver Endo vs Liver Epi
```{r}

liver_endopi_markers_wells = makeAnalysis(liverEndo, liverEpi)

write.table(liver_endopi_markers_wells, file = here("00_data_ingest", "sanne_analysis", "wells_analysis", paste("liver_endopi_markers_wells", ".tsv", sep="")) ,quote=FALSE, sep='\t')

```

## Lung Endo vs Lung Epi
```{r}

lung_endopi_markers_wells = makeAnalysis(lungEndo, lungEpi)

write.table(lung_endopi_markers_wells, file = here("00_data_ingest", "sanne_analysis", "wells_analysis", paste("lung_endopi_markers_wells", ".tsv", sep="")) ,quote=FALSE, sep='\t')

```

# Analysis same organ, endo vs rest+epi

## Aorta Endo

```{r}

aorta_endo_rest_markers_wells = makeAnalysis(aortaEndo, unique(c(allAorta, aortaEpi)))

write.table(aorta_endo_rest_markers_wells, file = here("00_data_ingest", "sanne_analysis", "wells_analysis", paste("aorta_endo_rest_markers_wells", ".tsv", sep="")) ,quote=FALSE, sep='\t')

```
## Bladder Endo

```{r}

bladder_endo_rest_markers_wells = makeAnalysis(bladderEndo, unique(c(allBladder, bladderEpi)))

write.table(bladder_endo_rest_markers_wells, file = here("00_data_ingest", "sanne_analysis", "wells_analysis", paste("bladder_endo_rest_markers_wells", ".tsv", sep="")) ,quote=FALSE, sep='\t')

```

## Kidney Endo

```{r}

kidney_endo_rest_markers_wells = makeAnalysis(kidneyEndo, unique(c(allKidney, kidneyEpi)))

write.table(kidney_endo_rest_markers_wells, file = here("00_data_ingest", "sanne_analysis", "wells_analysis", paste("kidney_endo_rest_markers_wells", ".tsv", sep="")) ,quote=FALSE, sep='\t')

```

## Lint Endo

```{r}

lint_endo_rest_markers_wells = makeAnalysis(lintEndo, unique(c(allLint, lintEpi)))

write.table(lint_endo_rest_markers_wells, file = here("00_data_ingest", "sanne_analysis", "wells_analysis", paste("lint_endo_rest_markers_wells", ".tsv", sep="")) ,quote=FALSE, sep='\t')

```

## Liver Endo

```{r}

liver_endo_rest_markers_wells = makeAnalysis(liverEndo, unique(c(allLiver, liverEpi)))

write.table(liver_endo_rest_markers_wells, file = here("00_data_ingest", "sanne_analysis", "wells_analysis", paste("liver_endo_rest_markers_wells", ".tsv", sep="")) ,quote=FALSE, sep='\t')

```

## Lung Endo

```{r}

lung_endo_rest_markers_wells = makeAnalysis(lungEndo, unique(c(allLung, lungEpi)))

write.table(lung_endo_rest_markers_wells, file = here("00_data_ingest", "sanne_analysis", "wells_analysis", paste("lung_endo_rest_markers_wells", ".tsv", sep="")) ,quote=FALSE, sep='\t')

```